---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# diskurs

<!-- badges: start -->
<!-- badges: end -->

diskurs (German for discourse) is an R package to handle data on discourse networks in a very specific form.

The main goal of the package is to ensure validated data loading and basic transformations of discourse in graph structure as introduced in the (sustainability.discourses)[sustainability.discourses] project.

At the moment, it mainly exists to facilitate the reproduction of analyses conducted within the [sustainability.discourses](sustainability.discourses.ch) project. The eventual goal is to hopefully support anyone working with a similar data structure in the future.

`diskurs` is in most cases a thin wrapper or special use case around [tidygraph](https://tidygraph.data-imaginist.com) and [igraph](https://igraph.org).

## Installation

You can install the development version of diskurs from [the r-universe builds of diskurs](https://urban-sustainability-lab-zurich.r-universe.dev/diskurs) with:

``` r
install.packages('diskurs', repos = c('https://urban-sustainability-lab-zurich.r-universe.dev', 'https://cloud.r-project.org'))
```

## Getting started

Create a discourse graph object from an edgelist and nodelist:

```{r setup}
library(diskurs)
```

```{r}
example_edgelist <- diskurs::edgelist_example
example_nodelist <- diskurs::nodelist_example
```

```{r}
disc_g <- load_discourse_graph(edgelist = example_edgelist, nodelist = example_nodelist)
disc_g
```

More functionality is documented in the vignettes on:

- [Basic functionality](vignettes/basics.html)
