---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# diskurs

<!-- badges: start -->
<!-- badges: end -->

⚠️ This package is at a very early stage of development ⚠️

diskurs (German for discourse) is an R package to handle data on discourse networks in a very specific form.

The main goal of the package is to ensure validated data loading and basic transformations of discourse in graph structure as introduced in the [sustainability.discourses](sustainability.discourses.ch) project.

At the moment, it mainly exists to facilitate the reproduction of analyses conducted within the [sustainability.discourses](sustainability.discourses.ch) project. The eventual goal is to hopefully support anyone working with a similar data structure in the future.

`diskurs` is in most cases a thin wrapper or special use case around [tidygraph](https://tidygraph.data-imaginist.com) and [igraph](https://igraph.org).

## Installation

You can install the development version of diskurs from [the r-universe builds of diskurs](https://urban-sustainability-lab-zurich.r-universe.dev/diskurs) with:

``` r
install.packages('diskurs', repos = c('https://urban-sustainability-lab-zurich.r-universe.dev', 'https://cloud.r-project.org'))
```

# Basic functionality

```{r}
library(diskurs)
```


## Required data format

```{r}
example_edgelist <- diskurs::edgelist_example
example_nodelist <- diskurs::nodelist_example
```


```{r}
example_edgelist
```

```{r}
example_nodelist
```

## Creating a discourse graph

```{r}
disc_g <- load_discourse_graph(edgelist = example_edgelist, nodelist = example_nodelist)
disc_g
```

Let's look at it:

```{r, warning=FALSE}
disc_g |> plot()
```


In many cases, working with the igraph or tidygraph object is advisable

```{r}
disc_g |> get_igraph()
```

This makes it possible to use the entire ecosystem provided by igraph...

```{r}
disc_g |> 
  get_igraph() |> 
  plot()
```

... or tidygraph.

```{r}
disc_g |> 
  get_tbl_graph() |> 
  tidygraph::activate(nodes) |>
  dplyr::mutate(closeness = tidygraph::centrality_closeness())
```

## Aggregating a graph

Aggregating a discourse graph here means combining stance edges to weighted edges over time, possibly also keeping only the most prevalent category.

```{r}
disc_g |> aggregate_discourse_graph()
```

```{r, warning=FALSE}
disc_g |> aggregate_discourse_graph(keep_only_highest = TRUE) |> plot()
```

## Time slice of discourse graph

```{r}
start_date <- "2012-01-01"
end_date <- "2014-06-06"
disc_g |> 
  time_slice_graph(start_date = start_date, end_date = end_date) |> 
  get_tbl_graph()
```

```{r, warning=FALSE}
disc_g |> 
  time_slice_graph(start_date = start_date, end_date = end_date) |> 
  plot()
```
