---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Goals of the package

⚠️ This package is at a very early stage of development ⚠️

The main goal of the package is to ensure validated data loading and basic transformations of discourse in graph structure as introduced in the (sustainability.discourses)[sustainability.discourses] project.

The package will support replication of project results and hopefully supports anyone working with a similar data structure in the future.

`diskurs` is in most cases a thin wrapper or special use case of [tidygraph](https://tidygraph.data-imaginist.com) and [igraph](https://igraph.org).

```{r setup}
library(diskurs)
```

# Basic functionality

## Required data format

```{r}
example_edgelist <- diskurs::edgelist_example
example_nodelist <- diskurs::nodelist_example
```
dfas
```{r}
example_edgelist
```

```{r}
example_nodelist
```

## Creating a discourse graph


```{r}
disc_g <- load_discourse_graph(edgelist = example_edgelist, nodelist = example_nodelist)
disc_g
```

In many cases, working with the igraph or tidygraph object is advisable

```{r}
disc_g |> get_igraph()
```

This makes it possible to use the entire ecosystem provided by igraph...

```{r}
disc_g |> 
  get_igraph() |> 
  plot()
```

... or tidygraph.

```{r}
disc_g |> 
  get_tbl_graph() |> 
  tidygraph::activate(nodes) |>
  dplyr::mutate(closeness = tidygraph::centrality_closeness())
```


